{ \fontfamily{ptm}\selectfont First Order Nonsmooth Optimization: Algorithm Design, Analysis, Convergence, and Applications }

### 2024-12-22 Notebook LaTEX/Proposal/main.tex
>w<, changes

\section{Introduction}
    Let $\RR^n$ be the ambient space. We consider 
    \begin{align}
        \min_{x \in \RR^n} \left\lbrace
            F(x): f(x) + g(x)
        \right\rbrace.
    \end{align}\label{eqn:additive-comp-obj}
    Unless specified, assume $f:\RR^n \rightarrow \RR$ is $L$-Lipscthiz smooth $\mu \ge 0$ strongly convex and $g:Q \rightarrow \overline \RR$ is convex. 
    This type of problem is referred to as additive composite problems in the literature. 
    \par
    Our ongoing research concerns accelerated proximal gradient type method for solving (\ref{eqn:additive-comp-obj}). 
    In the expository writing by Walkington \cite{noel_nesterovs_nodate}, a variant for of accelerated gradient method for strongly convex function $f$ is discussed. 
    We had two lingering questions after reading it. 
    \begin{enumerate}
        \item Do there exist a unified description for the convergence for both variants of the algorithm. 
        \item Is it possible to attain faster convergence rate without knowledge about the strong convexity of function $f$. 
    \end{enumerate}
    The good news is we have definitive answers for both questions by our own efforts of research. 
    Section \ref{sec:unify-nes-acceleration}, \ref{sec:spectral-momentum} are our ongoing research which present the answers to the questions. 
    \par
    In Section \ref{sec:unify-nes-acceleration}, we proposed the method of ``Relaxed Weak Accelerated Proximal Gradient (R-WAPG)'' as the foundation to describe several variants of Accelerated proximal gradient method in the literatures. 
    The convergence theories of R-WAPG allows us to model convergence of accelerated proximal gradient method where the momentum sequence doesn't strictly follow the conditions presented in the literatures. 
    The descriptive power of R-WAPG allows convergence analysis for all the variants using one single theorem. 
    \par
    In Section \ref{sec:spectral-momentum} we propose a practical algorithm that exploits a specific term in the proof of R-WAPG to achieve faster convergence for solving (\ref{eqn:additive-comp-obj}) without knowing parameter $L, \mu$ in prior. 
    Results of numerical experiments are presented. 
    \par
    Section \ref{sec:catalyst} are results of literatures review in MATH 590. 
    It's based on a series of papers (CITATION HERE) in the topic of Catalyst Meta Acceleration method for First Order Variance Reduced Methods. 
    We will point out potential future direction of research of Catalyst acceleration. 
    \par
    Section \ref{sec:pep}, \ref{sec:inexact-prox}, \ref{sec:nes-acc-ncnvx} preview literatures in  nonsmooth optimization frontier research where progress and impacts can be made.

\section{Preliminaries}
    Beck's book \cite{beck_first-order_2017}. 
    \subsection{Fundamentals in convex analysis}
    \subsection{Fundamentals in non-convex analysis}

\section{Unifying variants of Nesterov's accelerated methods}\label{sec:unify-nes-acceleration}

\section{Method Free R-WAPG}\label{sec:spectral-momentum}

\section{Catalyst accelerations and future works}\label{sec:catalyst}

@@

\section{Nestrov's acceleration in the non-convex case and momentum in general}\label{sec:nes-acc-ncnvx}

>>>>

\section{Introduction}
    Let $\RR^n$ be the ambient space. We consider 
    \begin{align}
        \min_{x \in \RR^n} \left\lbrace
            F(x): f(x) + g(x)
        \right\rbrace.
    \end{align}\label{eqn:additive-comp-obj}
    Unless specified, assume $f:\RR^n \rightarrow \RR$ is $L$-Lipscthiz smooth $\mu \ge 0$ strongly convex and $g:Q \rightarrow \overline \RR$ is convex. 
    This type of problem is referred to as additive composite problems in the literature. 
    \par
    Our ongoing research concerns accelerated proximal gradient type method for solving (\ref{eqn:additive-comp-obj}). 
    In the expository writing by Walkington \cite{noel_nesterovs_nodate}, a variant for of accelerated gradient method for strongly convex function $f$ is discussed. 
    We had two lingering questions after reading it. 
    \begin{enumerate}
        \item Do there exist a unified description for the convergence for both variants of the algorithms?
        \item Is it possible to attain faster convergence rate without knowledge about the strong convexity of function $f$?
        \item Is it possible to describe the convergence of function value for momentum sequences that are much weaker than the Nesterov's rule? 
    \end{enumerate}
    The good news is we have definitive answers for both questions by our own efforts of research. 
    Section \ref{sec:unify-nes-acceleration}, \ref{sec:spectral-momentum} are our ongoing research which present the answers to the questions. 
    \par
    In Section \ref{sec:unify-nes-acceleration}, we proposed the method of ``Relaxed Weak Accelerated Proximal Gradient (R-WAPG)'' as the foundation to describe several variants of Accelerated proximal gradient method in the literatures. 
    The convergence theories of R-WAPG allows us to model convergence of accelerated proximal gradient method where the momentum sequence doesn't strictly follow the conditions presented in the literatures. 
    The descriptive power of R-WAPG allows convergence analysis for all the variants using one single theorem. 
    \par
    In Section \ref{sec:spectral-momentum} we propose a practical algorithm that exploits a specific term in the proof of R-WAPG to achieve faster convergence for solving (\ref{eqn:additive-comp-obj}) without knowing parameter $L, \mu$ in prior. 
    Results of numerical experiments are presented. 
    \par
    Section \ref{sec:catalyst} are results of literatures review in MATH 590. 
    \todo{Add citations here. }{It's based on a series of papers} in the topic of Catalyst Meta Acceleration method for First Order Variance Reduced Methods. 
    We will point out potential future direction of research of Catalyst acceleration. 
    \par
    Section \ref{sec:pep}, \ref{sec:inexact-prox}, \ref{sec:nes-acc-ncnvx} preview literatures in  nonsmooth optimization frontier research where progress and impacts can be made.

\section{Preliminaries}
    \todoinline{
        Assumptions: Additive composite type convex objective until specified.  
    }
    \subsection{Fundamentals in convex analysis}
        \todoinline{
            Definitions: 
            \begin{enumerate}
                \item [$\square$]Strong convexity of a function. 
                \item [$\square$]The proximal gradient operator. 
                \item [$\square$]The proximal mapping operator. 
                \item [$\square$]The Bregman Divergence of function. 
            \end{enumerate}
            Lemmas: 
            \begin{enumerate}
                \item [$\square$]Quadratic growth conditions of a strongly convex function. 
                \item [$\square$]The proximal gradient envelope.
                \item [$\square$]A property of gradient mapping. 
            \end{enumerate}
            Theorems: 
            \begin{enumerate}
                \item [$\square$]The proximal gradient inequality, for additive composite objective where the smooth part is $\mu \ge 0$ strongly convex. 
            \end{enumerate}
        }

    \subsection{Fundamentals in non-convex analysis}

\section{Unifying variants of Nesterov's accelerated methods}\label{sec:unify-nes-acceleration}
    \todoinline{
        This section is really about stating the results of the draft paper and no explaining will be done here. 
        Along with the content of the draft paper, we will also explain the origin and inspirations of the ideas. 
    }
    \todoinline{
        Definitions:
        \begin{enumerate}
            \item Method of Nesterov's estimating sequence.
            \item R-WAPG Sequence.
            \item R-WAPG algorithm .
            \item R-WAPG Intermediate form.
            \item R-WAPG Similar triangle form. 
            \item R-WAPG Momentum form. 
        \end{enumerate}
    }
    \todoinline{
        Theorems: 
        \begin{enumerate}
            \item Convergence of the R-WAPG algorithm.
            \item R-WAPG First equivalent form. 
            \item R-WAPG Second equivalent form.
            \item R-WAPG Third equivalent form.
            \item Convergence with constant momentum. 
            \item Convergence with Chambolle, Dossal Sequences.
        \end{enumerate}
        Lemmas
        \begin{enumerate}
            \item Inverted FISTA sequence is a R-WAPG sequence.
            \item Constant R-WAPG sequence.
        \end{enumerate}
    }

\section{Method Free R-WAPG}\label{sec:spectral-momentum}
    \todoinline{
        Algorithm, and results of numerical experiments with their descriptions. 
    }
\section{Catalyst accelerations and future works}\label{sec:catalyst}
    \todoinline{\noindent
        Literatures review of the topics in Catalyst acceleration method. 
        Here is a list of topics: 
        \begin{enumerate}
            \item The original accelerated PPM. 
            \item The Catalyst with weakly convex objectives. 
        \end{enumerate}
        After the literature reviews of the core literatures, move on and state new research directions and open problems.     
    }
    \todoinline{\noindent
        A list of relevant literatures: 
        \begin{enumerate}
            \item 
        \end{enumerate}
    }

@@

\section{Nestrov's acceleration in the non-convex case}\label{sec:nes-acc-ncnvx}
